### 2018-03-26 Sections/cryptowars.tex
Crypto comments from gavin

The mining process is based upon the computational hardness of inverting SHA256 hashing\index{Hash functions}\index{SHA256}. A legitimate Bitcoin is defined by a string with a hash satisfying a thoughtfully chosen constraint, specifically one which hashes to a value within some range,
\begin{align}
	y_\text{lower}\leq f_\text{hash}(x_\text{coin}) \leq y_\text{upper}.
\end{align}
This is slightly weaker than inverting hash functions, but is nonetheless a task that can only be approached via brute-force hashing in the forward direction. This associates computational complexity with the mining process, and hence computational integrity of the money supply, whilst upper bounding the number of unique coins that can exist.

@@

For these reasons, this scheme lends itself readily to photonic implementation, provided a reliable GHZ preparation circuit. The scheme has since been ported to operate on toric codes\index{Toric code} to facilitate error correction of the distributed GHZ states.

>>>>

The mining process is based upon the computational hardness of inverting SHA256 hashing\index{Hash functions}\index{SHA256}. A legitimate Bitcoin is defined by a string with a hash satisfying a thoughtfully chosen constraint, specifically one which hashes to a value within some range,
\begin{align}
	y_\text{lower}\leq \text{SHA256}(\text{SHA256}(x_\text{coin})) \leq y_\text{upper}.
\end{align}
This is slightly weaker than inverting hash functions, but is nonetheless a task that can only be approached via brute-force hashing in the forward direction. This associates computational complexity with the mining process, and hence computational integrity of the money supply, whilst upper bounding the number of unique coins that can exist.

@@

For these reasons, this scheme lends itself readily to photonic implementation, provided a reliable GHZ preparation circuit. The scheme has since been ported to operate on distributed toric codes\index{Toric code} to facilitate error correction of the distributed GHZ states \cite{GavinMeni}.
